A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-11 sanity/paper1.tex
Recommendations
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1057 43ef1190-90fd-4dd7-a769-d0121f02b80e

Based on the results of DyLDO, it is highly likely that most cache
prohibitions are misguided, and server administrators are advised to
turn them off unless they are sure they are required.\todo{split this
  in the stuff that follows}

@@

\paragraph*{Acknowledgements} The author would like to thank Jürgen
Umbrich and Martin Giese for careful review and critical comments, and
Gregory Todd Williams for promptly solving issues in the underlying
libraries used in this study, Axel Polleres for encouraging comments
and Jonas Smedegaard for proofreading.

>>>>

It is mainly the objective of this paper to be descriptive, but from
the results of this study and on the results of DyLDO, we note that it
is highly likely that most cache prohibitions are misguided, and
server administrators are advised to turn them off unless they are
sure they are required.

Additionally, based in part on the survey, but also on other practical
experience, we suggest the following:

@@

\paragraph*{Acknowledgements} The author would like to thank Jürgen
Umbrich and Martin Giese for careful review and critical comments, and
Gregory Todd Williams for promptly solving issues in the underlying
libraries used in this study, Axel Polleres for encouraging comments
and Jonas Smedegaard for proofreading. We also thank the anonymous
reviewers for extensive reviews.
